Supplementary information

### 2019-12-15 manuscript/supplementary.Rmd
increased size of numeric descriptor plots
finished descriptor table

phenotypic_descriptor_info %>%
  kable(format = 'latex',booktabs = TRUE,longtable = TRUE) %>%
  kable_styling(latex_options = 'repeat_header',repeat_header_continued = TRUE) %>%
  column_spec(1,width = '1.5cm') %>%
  column_spec(2,width = '3cm') %>%
  column_spec(4:5,width = '7cm') %>%
  collapse_rows(columns = 1,latex_hline = "major", valign = "middle") %>%
  landscape()
```

@@

```{r PDInumeric,fig.height=8}
loadd(descriptor_scatter_plots)

@@

```{r DAInumeric,fig.height=8}
descriptor_scatter_plots$DAI_numeric
```

>>>>

phenotypic_descriptor_info %>%
  select(-`Descriptor Type`,-`Data Type`) %>%
  kable(format = 'latex',booktabs = TRUE,longtable = TRUE) %>%
  kable_styling(latex_options = c('striped','repeat_header'),repeat_header_continued = TRUE) %>%
  # column_spec(1,width = '1.5cm') %>%
  column_spec(1,width = '3cm') %>%
  column_spec(2:3,width = '6cm') #%>%
  # collapse_rows(columns = 1,latex_hline = "major", valign = "middle")
```

@@

```{r PDInumeric,fig.height=9}
loadd(descriptor_scatter_plots)

@@

```{r DAInumeric,fig.height=9}
descriptor_scatter_plots$DAI_numeric
```
